### 2022-07-02 chapters/benchmarking/draft.tex
refactoring

\section{Introduction}
To optimize the software energy consumption, a reproducible setup environment requires to be designed.

This chapter will be dedicated to provide a set of guidelines to provide a \em{reproducible, accurate} and \em{representative} tests. Each aspect will be detailed in the sections below.

@@

A successful benchmark has three criterions to fullfil.
First, it has to be \emph{reproducible} for others to replicate.
Second, the results should be \emph{accurate}, which means each time we rerun the benchmark we are expecting the same results.
Finally, it should \emph{represent} the real world.
In other words, the conclusions brought from the experiment should be valid outside the experimentation as well.
In my case, the real world is the production environment.
Therefore, our experiments should reflect what is happening in the production environments.
In this section, I will deeper dig in each aspect, present what has been done by others and my contributions, and finally I will propose some perspectives, to improve such experiments.

@@

\subsection{Reproducibility}
One of the most difficult challenges faced by researchers is the reproducibility of their benchmarks.
Actually, many results fail to be reproduced,\footnote{Trouble at the lab, The Economist, 19 October 2013;  www.economist.com/news/briefing/ 21588057-scientists-think-science-self-correcting- alarming-degree-it-not-trouble.} which led to a \emph{replication crisis}.
As this crisis hit most of the empirical studies, most of the reviews now includes reproducibility as one of the minimal standard for judging scientific merit.\cite{peng2011reproducible}
One of the criterions supporting reproducibility is the publication of the dataset and the algorithms run on the raw data to conclude the results.
There is even some disagreement about what the terms "reproducibility" or "replicability" by themselves mean \cite{goodman2016does}.
According to \cite{echtler2018open}, \emph{replicability} extends \emph{reproducibility} with the ability to collect a new raw dataset comparable to the original one by re-executing the experiment under similar condition, instead of just the ability to get the same results by running the statistical analyses on the original data set.

@@

In addition to those benchmarks, a new category of benchmarking technique emerged to simulate the worst case of the production environments, inlcuding performance tests, which are benchmarks meant to evaluate the behavior of a software under stress situations.
We can cite as an example the Gatling for web application and stress-ng for hardwares.%ROMAIN: Add citations.
%% YEP I KNOW, THIS IS JUST FOR ME TO READ IT LATER AND GIVE A BETTER CONTEXT
%% sorry caps ^^"

>>>>

\section{Introduction}
A reproducible setup environment needs to be established in order to maximize the software's potential to reduce energy consumption.

This chapter will be devoted to giving a set of guidelines with the intention of delivering a test that is accurate, representative, and replicable.

% This chapter will go over each component in further detail, describe it, and explain how it is used in the field of empirical analysis for software energy optimization.

@@

A successful benchmark must meet three criteria.
First, it must be \textbf{reproducible} in order for others to imitate it.
Second, the findings should be \textbf{accurate},which implies that we should expect the same results each time we run the benchmark.
Finally, it should \textbf{represent} reality.
In other words, the experiment's findings should be applicable outside of the research lab as well.
The aim of \textbf{representativeness} in this thesis is the manufacturing environment.
As a result, the experiments should reflect what happens in production contexts.

@@

\subsection{Reproducibility}
The reproducibility of experiments is often ranked as one of the most difficult difficulties faced by researchers. In point of fact, many of the outcomes cannot be duplicated.,\footnote{Trouble at the lab, The Economist, 19 October 2013;  www.economist.com/news/briefing/ 21588057-scientists-think-science-self-correcting- alarming-degree-it-not-trouble.} which led to a \emph{replication crisis}.
As this crisis hit most of the empirical studies, most of the reviews now includes reproducibility as one of the minimal standard for judging scientific merit.\cite{peng2011reproducible}
One of the criterions supporting reproducibility is the publication of the dataset and the algorithms run on the raw data to conclude the results.
There is even some disagreement about what the terms "reproducibility" or "replicability" by themselves mean \cite{goodman2016does}.
According to \cite{echtler2018open}, \emph{replicability} extends \emph{reproducibility} with the ability to collect a new raw dataset comparable to the original one by re-executing the experiment under similar condition, instead of just the ability to get the same results by running the statistical analyses on the original data set.

@@

In addition to these benchmarks, a new category of testing techniques has emerged to simulate the worst cases of the production environments. This new category of benchmarking called performance tests\cite{pradeep2019pragmatic}, which are benchmarks meant to evaluate the behavior of software under stress situations. We can use the Gatling\footnote{\url{https://gatling.io/}} as an illustration for web applications stresser and stress-ng for hardware heavy workload perormance measurements~\cite{king2017stress}.

\subsection{Extension}
Morover, The field of computer science is seeing rapid advancements, which has led to an increase in the number of obsolete results. Even more so, when it comes to studies that compare multiple solutions, it is impossible to cover them all.
In addition, between the preliminary experiment and the results that were published, there may have been the appearance of new candidates as well as the development of others. As a result, we would like to provide a fresh idea for a productive experiment that we will call "Extension." The ability to give the required tools to not only repeat the experiment but also to add additional candidates, workloads, or key metrics.

\subsection{conclusion}

We propose making certain enhancements to the benchmarking framework that was suggested by the collaboratory on Experimental Evaluation of Software \footnote{\url{http://evaluate.inf.usi.ch/}}. and Systems in Computer Science in order to address those problems.
Instead of only presenting the four primary aspects of their guidelines, which are \emph{measurement contexts} that indicate the software and hardware components that will alter or remain constant during the experiment. \emph{workloads} which identify the benchmarks to use in the experiment, as well as their inputs; \emph{metrics} that specify the attributes to be measured and how to assess them. \emph{Data analysis} show how to examine data and evaluate the outcomes of the analysis to offer insight into the assertions that arise from the study.

\begin{itemize}
    \item \textbf{candidates}: a set of candidates that will be used in the experiment. The candidates should be agnostic of the experiment context and they all
\end{itemize}

\begin{figure}%[!htb]
    \center{\includegraphics[width=.9\linewidth]{imgs/benchmarkingprotocol}}
    \caption{Benchmarking protocol}\label{fig:benchmarkingprotocol}
\end{figure}

### 2022-07-02 chapters/benchmarking/reproducibility.tex
add : python
refactoring

%  State of the art. 
%  TODO :

@@

\paragraph{Studying Hardware Factors.}
This variation has often been related to the manufacturing process~\cite{coles_comparing_2014}, but has also been a subject of many studies, considering several aspects that could impact and vary the energy consumption across executions and on different chips.
On the one hand, the correlation between the processor temperature and the energy consumption was one of the most explored paths.
Kistowski~\emph{et~al.} showed in~\cite{joakim_v_kisroski_variations_2016} that identical processors can exhibit significant energy consumption variation with no close correlation with the processor temperature and performance.
On the other hand, the authors of~\cite{wang_potential_2018} claimed that the processor thermal effect is one of the most contributing factors to the energy variation, and the CPU temperature and the energy consumption variation are tightly coupled.

\note{add the corelation value}

This exposes the processor temperature as a delicate factor to consider while comparing energy consumption variations across a set of homogeneous processors.%, but also, if a same workload can cause the CPUs to reach different temperatures.

The ambient temperature was also discussed in many papers as a candidate factor for the energy variation of a processor.
In~\cite{ranka_energy_2009}, the authors claimed that energy consumption may vary due to fluctuations caused by the external environment.
These fluctuations may alter the processor temperature and its energy consumption.
However, the temperature inside a data center does not show major variations from one node to another.
In~\cite{el_mehdi_diouri_your_2013}, El~Mehdi~Dirouri~\emph{et~al.} showed that switching the spot of two servers does not affect their energy consumption.
Moreover, changing hardware components, such as the hard drive, the memory or even the power supply, does not affect the energy variation of a node, making it mainly related to the processor.
This result was recently assessed by~\cite{wang_potential_2018}, where the rack placement and power supply introduced a maximum of $2.8\,\%$ variation in the observed energy consumption.

Beyond hardware components, the accuracy of power meters has also been questioned.
Inadomi~\emph{et~al.}~\cite{inadomi_analyzing_2015} used three different power measurement tools: RAPL, Power Insight\footnote{\url{https://www.itssolution.com/products/trellis-power-insight-application}} and BGQ EMON.
All of the three tools recorded the same $10\,\%$ of energy variation, that was supposedly related to the manufacturing process.
%% this is to prove that the problem is REAL !!!

\paragraph{Mitigating Energy Variations.}
Acknowledging the energy variation problem on processors, some papers proposed contributions to reduce and mitigate this variation.
In~\cite{inadomi_analyzing_2015}, the authors introduced a variation-aware algorithm that improves application performance under a power constraint by determining module-level (individual processor and associated DRAM) power allocation, with up to $5.4\times$ speedup.
The authors of~\cite{hammouda_noise-tolerant_2015} proposed parallel algorithms that tolerate the variability and the non-uniformity by decoupling per process communication over the available CPU.
Acun~\emph{et~al.}~\cite{acun_variation_2016} found out a way to reduce the energy variation on Ivy~Bridge and Sandy~Bridge processors, by disabling the Turbo~Boost feature to stabilize the execution time over a set of processors.
They also proposed some guidelines to reduce this variation by replacing the old---slower---chips, by load balancing the workload on the CPU cores and leaving one core idle.
They claimed that the variation between the processor cores is insignificant.
In~\cite{chasapis_runtime-guided_2016}, the researchers showed how a parallel system can be used to deal with the energy variation by compensating the uneven effects of power capping.

In~\cite{marathe_empirical_2017_m}, the authors highlight the increase of energy variation across the latest Intel micro-architectures by a factor of $4$ from Sandy~Bridge to Broadwell, a $15\,\%$ of run-to-run variation within the same processor and the increase of the inter-cores variation from $2.5\,\%$ to $5\,\%$ due to hardware-enforced constraints, concluding with some recommendations for Broadwell usage, such as running one hyper-thread per core.
%  NOTE :/this might be interesting for greeFaaS

\subsection*{Objective}
While the state of the art aims to create a large umbrella that covers all empirical benchmarks related to computer science, we rather aim to narrow our study to energy benchmarking only.
In other words, we will focus on pitfalls that hinders the energy claims of software.
We are clearly aware of the impact of hardware on energy variations.
However, we believe that there is still a room to control this energy variation for practitioners by using only parameters that can be tuned.
To do so, we have inducted a set of empirical experiments using the guidelines provided by state of the art, to determine which controllable factors can reduce the variation of the energy consumption of benchmarks.
We will first start with evaluating the parameters mentioned by \cite{heinrich_predicting}.

% introduction of vms 
\subsection{Virtualisation}
To resolve this problem, practitioners tend to use Virtualisation. Using virtual machines aka VM gives reaserchers the freedom to choose their own tools, software and operating system that they are the most confortable with without paying the price to change the actual working environment, which will give them eventually more controle over the dependencies and the execution environement. Moreover, using a vm will solve the \emph{replication crisis} thanks to the virtual images, even the most complex architecture can be reproduced easily by just instantiating a copy of the image. Since the virtual machines are agnostic to the host architecture, reaserchers won't have to worry about where and how their experiments are replicated because they have already setup the execution environement. Another advantage to the virtual machines is the snapshot mechanism, it allows reaserchers to create backups and revert some changes with simple clicks. Last but not least,thanks to the isolation, virtual machines push the reproducibility further by allowing the future usages to see all the variables -controled and uncontroled-  and do other analysis without dealing with any dependencies. In his paper \cite{howe_virtual_2012} bill howe lists the advantages of using virtual machines in reaserchers experements including the economical impact and cultural limitation to a such approach.

@@

%  basically just rephrase the paper

\subsection{docker and accuracy}
%% TODO : add an introduction, maybe some more details 
And now Since the stat of the art has aggreed on the impact of docker on the energy consumption,Let's discuss it's impact on the accuracy. In other words\\
\textbf{RQ :} does Docker affect the energy variation of the exepements ?

>>>>

%  State of the art.

@@

\section{Reproducibility in benchmarking }

%% just a placeholder title for the moment 
% introduction of vms

\subsection{Virtual machines}
To resolve this problem, practitioners tend to use Virtualisation. Using virtual machines aka VM gives reaserchers the freedom to choose their own tools, software and operating system that they are the most confortable with without paying the price to change the actual working environment, which will give them eventually more controle over the dependencies and the execution environement. Moreover, using a vm will solve the \emph{replication crisis} thanks to the virtual images, even the most complex architecture can be reproduced easily by just instantiating a copy of the image. Since the virtual machines are agnostic to the host architecture, reaserchers won't have to worry about where and how their experiments are replicated because they have already setup the execution environement. Another advantage to the virtual machines is the snapshot mechanism, it allows reaserchers to create backups and revert some changes with simple clicks. Last but not least,thanks to the isolation, virtual machines push the reproducibility further by allowing the future usages to see all the variables -controled and uncontroled-  and do other analysis without dealing with any dependencies. In his paper \cite{howe_virtual_2012} bill howe lists the advantages of using virtual machines in reaserchers experements including the economical impact and cultural limitation to a such approach.

@@

\subsection{docker and accuracy}
And now Since the stat of the art has aggreed on the impact of docker on the energy consumption,Let's discuss it's impact on the accuracy. In other words\\
\textbf{RQ :} does Docker affect the energy variation of the exepements ?
